### 2019-03-09 README.Rmd
update

### Compendium URL

### Authors

@@

### Contents

@@

### How to use

#### Read the code, access the data

@@

#### Install the R package

@@

```{r README-1, eval = FALSE}
packrat::restore()
source("analysis/drake.R")
make(plan, keep_going = TRUE, console_log_file = stdout()) 
# use more cores with make(plan, jobs = <number of cores>)
```

## Runtime

Predicted total runtime (based on all target runtimes ever built and stored in the internal `config` file)

```{r README-2 }
source("analysis/drake.R")
predict_runtime(config, from_scratch = TRUE)
```

Acceleration when parallelizing the `make()` call

```{r README-3, warning=FALSE, message=FALSE}
time <- c()
for (jobs in 1:10){
time[jobs] <- predict_runtime(
drake_config(),
jobs = jobs,
from_scratch = TRUE,
known_times = build_times(targets_only = TRUE)$elapsed
)
}

library(ggplot2)
ggplot(data.frame(time = time / 3600, jobs = ordered(1:10), group = 1)) +
geom_line(aes(x = jobs, y = time, group = group)) +
scale_y_continuous(breaks = 0:10 * 4, limits = c(0, 29)) +
ggpubr::theme_pubr() +
xlab("jobs argument of make()") +
ylab("Predicted runtime of make() (hours)")
```

### Licenses

@@

### Notes and resources

@@

## Literature

>>>>

**title**

# Authors

@@

# Contents

@@

# How to use

## Read the code, access the data

@@

## Install the R package

@@

```{r README-1, eval = FALSE}
packrat::restore()
r_make()
```

# Runtime

Predicted total runtime.
The time is based on all targets that have been created so far in the project.
Estimated time will differ depending on the CPU speed and possible availability of a HPC.

```{r README-2 }
r_predict_runtime()
```

# Licenses

@@

# Notes and resources

@@

# Literature
